---
title: "How it works"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How it works}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_knit$set(
  root.dir = ".."
)
```

![](https://img.shields.io/badge/status-under_development-red)

```{r pkgs}
library(raiden)
library(rstudioapi)
library(rlang)
library(R6)
```

## Outline

This vignette documents how the `raiden` Addin locates your R objects, determines their structure, and provides the UI interface for editing the `roxygen2` tags.

## `is.package`?

Is the current directory an R package? 

```{r}
getwd()
is_package()
```

## Load objects 

Let's load some objects in the global environment:

```{r}
my_list <- list('mtcars' = datasets::mtcars,
                'attitude' = datasets::attitude,
               'titanic' = datasets::Titanic)
mtcars <- datasets::mtcars
my_time <- Sys.time()
R6_class_generator <- R6Class()
R6_object <- R6_class_generator$new()
```


The `gather_objects()` function will find all objects in the global environment. 

```{r}
gather_objects(type = "all")
```

The `gather_classes()` will identify all objects in the global environment, but also return their class: 

```{r}
gather_classes()
```

In the case that an object has multiple classes, the `gather_classes()` collapses these into a single character (separated by a comma (`,`)):

